SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-09-11 scipy-1.0/paper.tex
MAINT: review comments in PR 245
* restore PyPy compatibility statement with 1.0
release point qualifier

* move discussion of GPU support / scipy.fft to final
section of manuscript instead of language section

* describe scipy.fft as a subpackage instead of submodule

The position that SciPy occupies near the
foundation of the scientific Python ecosystem is such that adoption of new
languages or major dependencies is generally unlikely---our choices are strongly
driven by long-term stability. GPU acceleration, new transpiling libraries, and
the latest JIT compilation approaches (i.e.,
Numba\cite{Lam:2015:NLP:2833157.2833162}) are very powerful, but have traditionally fallen
outside the remit of the main SciPy library. That said, we have recently
increased our efforts to support compatibility with some of these options, and
while the exact approach we will adopt across the entire library remains unclear,
we do now have a concrete implementation of a submodule that allows for the experimental
use of multiple backends such as GPU-tractable data structures in the new
\texttt{scipy.fft}. This will be described in detail in a future report.

@@

>>>>

The position that SciPy occupies near the
foundation of the scientific Python ecosystem is such that adoption of new
languages or major dependencies is generally unlikely---our choices are strongly
driven by long-term stability. GPU acceleration, new transpiling libraries, and
the latest JIT compilation approaches (i.e.,
Numba\cite{Lam:2015:NLP:2833157.2833162}) are very powerful, but have traditionally fallen
outside the remit of the main SciPy library. That said, we have recently
increased our efforts to support compatibility with some of these options, and
our full test suite passed with the PyPy JIT compiler\cite{Bolz:2009:TMP:1565824.1565827}
at the 1.0 release point.

@@

A final important challenge to address is the accommodation of GPU and distributed
computing without disrupting our conventional and heavily-used algorithm / API
infrastructure. While the exact approach we will adopt across the entire library
to leverage these emerging technologies remains unclear, and was not a priority
at the 1.0 release point, we do now have a concrete implementation of a subpackage
that allows for the experimental use of multiple backends, such as GPU-tractable
data structures, in the new \texttt{scipy.fft}. This will be described in detail
in a future report.
